PaperMelanoma

### 2022-06-30 Code/PaperMelanoma.Rmd
C-index negative and positive seperate added

#### Melanoma specific mortality (MSM)
```{r, eval=TRUE}
sel.data$MSM<-1*(sel.data$Status=="DOD")
```

@@

# Test non-lineairities
### Test if Age should be modelled non-linearly
```{r, eval=TRUE}
form.linear.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  Breslow +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  Rdamcrit +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:Breslow +
  SNstatus:multiple.fields
form.nonlinear.age.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  log(Age.SN) +
  Ulceration +
  Loc_CAT +
  Histology +
  Breslow +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  Rdamcrit +
  Dewar +
  SNstatus:Sex +
  SNstatus:log(Age.SN) +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:Breslow +
  SNstatus:multiple.fields
linear.full.Rec <- Hmisc::fit.mult.impute(form.linear.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
nonlinear.age.full.Rec <- Hmisc::fit.mult.impute(form.nonlinear.age.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# distribution of Age
hist(last.imputed.data.set$Age.SN)
# linear model
linear.full.Rec$loglik[2]
# using log(Age) gives slightly better log likelihood
nonlinear.age.full.Rec$loglik[2]
```

### Test if Breslow should be modelled non-linearly
```{r, eval=TRUE}
form.nonlinear.Breslow.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  log(Breslow) +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  Rdamcrit +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:log(Breslow) +
  SNstatus:multiple.fields
nonlinear.Breslow.full.Rec <- Hmisc::fit.mult.impute(form.nonlinear.Breslow.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# distribution of Breslow
hist(last.imputed.data.set$Breslow)
# linear model
linear.full.Rec$loglik[2]
# using log(Breslow) gives better log likelihood
nonlinear.Breslow.full.Rec$loglik[2]
```

### Test if Rdamcrit should be modelled non-linearly
```{r, eval=TRUE}
form.nonlinear.Rdamcrit.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  Breslow +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  log(Rdamcrit) +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:Breslow +
  SNstatus:multiple.fields
nonlinear.Rdamcrit.full.Rec <- Hmisc::fit.mult.impute(form.nonlinear.Rdamcrit.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# distribution of Rdamcrit
hist(last.imputed.data.set$Rdamcrit)
# linear model
linear.full.Rec$loglik[2]
# using log(Rdamcrit) gives better log likelihood
nonlinear.Rdamcrit.full.Rec$loglik[2]
```

# Full model for recurrence
```{r, eval=TRUE}
form.full.Rec.5 <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  log(Breslow) +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  log(Rdamcrit) +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:log(Breslow) +
  SNstatus:multiple.fields
f.mi.full.Rec.5 <- Hmisc::fit.mult.impute(form.full.Rec.5, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# stats::anova(f.mi.full.Rec.5)
summary(f.mi.full.Rec.5, Tot_SNs_pos=c(0, 1))
```

# Final model for recurrence selected by backward selection with p = 0.01
```{r, eval=TRUE}
c.Breslow <- mean(log(last.imputed.data.set$Breslow))
form.BS.Rec.5 <- S.Rec.5 ~
  SNstatus +
  Age.SN +
  Ulceration +
  Loc_CAT +
  I(log(Breslow)-c.Breslow) +
  log(Rdamcrit) +
  SNstatus:I(log(Breslow)-c.Breslow)
f.mi.BS.Rec.5 <- Hmisc::fit.mult.impute(form.BS.Rec.5,cph,xtrans=imputed.data,data=data.to.be.imputed,n.impute=m,
                           pr=FALSE,fit.reps=TRUE,y=TRUE,x=TRUE,se.fit=TRUE)
summary(f.mi.BS.Rec.5, Breslow=exp(c.Breslow))
coef(f.mi.BS.Rec.5)
# round(stats::anova(f.mi.BS.Rec.5)[order(stats::anova(f.mi.BS.Rec.5)[, 'P']),], 3)
stats::anova(f.mi.BS.Rec.5)
```

# Refitted full model for melanoma specific mortality
```{r, eval=TRUE}
form.full.MSM.5.refit <- S.MSM.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  log(Breslow) +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  log(Rdamcrit) +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:log(Breslow) +
  SNstatus:multiple.fields
f.mi.full.MSM.5.refit <- Hmisc::fit.mult.impute(form.full.MSM.5.refit,cph,xtrans=imputed.data,data=data.to.be.imputed,n.impute=m,
                                 pr=FALSE,fit.reps=TRUE,y=TRUE,x=TRUE,se.fit=TRUE)
f.mi.full.MSM.5.refit
summary(f.mi.full.MSM.5.refit, Tot_SNs_pos=c(0, 1))
stats::anova(f.mi.full.MSM.5.refit)
```

# Refitted final model for melanoma specific mortality
```{r, eval=TRUE}
form.BS.MSM.5.refit <- S.MSM.5 ~
  SNstatus +
  Age.SN +
  Ulceration +
  Loc_CAT +
  I(log(Breslow)-c.Breslow) +
  log(Rdamcrit) +
  SNstatus:I(log(Breslow)-c.Breslow)
f.mi.BS.MSM.5.refit <- Hmisc::fit.mult.impute(form.BS.MSM.5.refit,cph,xtrans=imputed.data,data=data.to.be.imputed,n.impute=m,
                                  pr=FALSE,fit.reps=TRUE,y=TRUE,x=TRUE,se.fit=TRUE)
# round(anova(f.mi.BS.MSM.5.refit)[order(anova(f.mi.BS.MSM.5.refit)[, 'P']),], 3)
f.mi.BS.MSM.5.refit
summary(f.mi.BS.MSM.5.refit, Breslow=exp(c.Breslow))
stats::anova(f.mi.BS.MSM.5.refit)
```

# Calibrated final model for melanoma specific mortality
Fit disease specific mortality to the linear predictor of recurrence
```{r, eval=TRUE}
lp.BS<-f.mi.BS.Rec.5$linear
f.mi.BS.MSM.5<-rms::cph(S.MSM.5~lp.BS,y=TRUE,x=TRUE)
MSM.cal.fact <- stats::coef(f.mi.BS.MSM.5)
MSM.cal.fact
stats::confint(f.mi.BS.MSM.5)
utils::write.table(paste0(sprintf("%.2f", stats::coef(f.mi.BS.MSM.5)), " [",
            sprintf("%.2f", as.numeric(stats::confint(f.mi.BS.MSM.5))[1]), "; ",
            sprintf("%.2f", as.numeric(stats::confint(f.mi.BS.MSM.5))[2]), "]"),
            file='Z:/Project Melanoom/PaperMelanoma/Results/calibration.MSS.txt', 
            row.names=FALSE, col.names=FALSE, sep=",")
```

@@

@@

# save for Rshiny app
coef.Rec <- stats::coef(f.mi.BS.Rec.5)
center.Rec <- f.mi.BS.Rec.5$center
save(h0.Rec, h0.MSM, coef.Rec, c.Breslow, center.Rec,
     file=paste0('Z:/Project Melanoom/PaperMelanoma/Results/h0.Rec.MSM.Rdata'), compress=TRUE)
load(file=paste0('Z:/Project Melanoom/PaperMelanoma/Results/h0.Rec.MSM.Rdata'))
```

@@

#### Example to check probabilities with app
```{r, eval=TRUE}
patient.nr <- 115 # 395 and 396 = Negative, 397 and 398 = Positive, 30 = Head & neck, 115 has large Breslow
data.to.be.imputed[patient.nr, c("SNstatus", "Age.SN", "Ulceration", "Loc_CAT", "Breslow", "Rdamcrit")]
lp.score.Rec.true <- predict(f.mi.BS.Rec.5)[patient.nr]
lp.score.Rec.try <- predict(f.mi.BS.Rec.5, newdata=data.frame(SNstatus=data.to.be.imputed[patient.nr,"SNstatus"],
                                                            Age.SN=data.to.be.imputed[patient.nr,"Age.SN"],
                                                            Ulceration=data.to.be.imputed[patient.nr,"Ulceration"],
                                                            Loc_CAT=data.to.be.imputed[patient.nr,"Loc_CAT"],
                                                            Breslow=data.to.be.imputed[patient.nr,"Breslow"],
                                                            Rdamcrit=data.to.be.imputed[patient.nr,"Rdamcrit"]),
                                                            type="lp")
p.Rec.example <- fun.event(lp=lp.score.Rec.try, h0=h0.Rec)
p.MSM.example <- fun.event(lp=lp.score.Rec.try, h0=h0.MSM)

>>>>

#### Melanoma specific mortality (MSM)
```{r, eval=TRUE}
# 504 patients died due to melanoma, 102 patients died from other causes
table(sel.data$Status, sel.data$dead)
sel.data$MSM<-1*(sel.data$Status=="DOD")
```

@@

# Test non-lineairities
### Test if Age should be modelled non-linearly
```{r, eval=TRUE}
form.linear.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  Breslow +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  Rdamcrit +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:Breslow +
  SNstatus:multiple.fields
form.nonlinear.age.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  rcs(Age.SN) +
  Ulceration +
  Loc_CAT +
  Histology +
  Breslow +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  Rdamcrit +
  Dewar +
  SNstatus:Sex +
  SNstatus:rcs(Age.SN) +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:Breslow +
  SNstatus:multiple.fields
linear.full.Rec <- Hmisc::fit.mult.impute(form.linear.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
nonlinear.age.full.Rec <- Hmisc::fit.mult.impute(form.nonlinear.age.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# distribution of Age
hist(last.imputed.data.set$Age.SN)
# linear model
linear.full.Rec$loglik[2]
# using log(Age) gives slightly better log likelihood
nonlinear.age.full.Rec$loglik[2]
```

### Test if Breslow should be modelled non-linearly
```{r, eval=TRUE}
form.nonlinear.Breslow.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  rcs(Breslow) +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  Rdamcrit +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:rcs(Breslow) +
  SNstatus:multiple.fields
nonlinear.Breslow.full.Rec <- Hmisc::fit.mult.impute(form.nonlinear.Breslow.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# distribution of Breslow
hist(last.imputed.data.set$Breslow)
# linear model
linear.full.Rec$loglik[2]
# using log(Breslow) gives better log likelihood
nonlinear.Breslow.full.Rec$loglik[2]
# test
anova(nonlinear.Breslow.full.Rec)
```

### Test if Rdamcrit should be modelled non-linearly
```{r, eval=TRUE}
form.nonlinear.Rdamcrit.full.Rec <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  Breslow +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  rcs(Rdamcrit) +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:Breslow +
  SNstatus:multiple.fields
nonlinear.Rdamcrit.full.Rec <- Hmisc::fit.mult.impute(form.nonlinear.Rdamcrit.full.Rec, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
# distribution of Rdamcrit
hist(last.imputed.data.set$Rdamcrit)
# linear model
linear.full.Rec$loglik[2]
# using log(Rdamcrit) gives better log likelihood
nonlinear.Rdamcrit.full.Rec$loglik[2]
```

# Full model for recurrence
```{r, eval=TRUE}
form.full.Rec.5 <- S.Rec.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  log(Breslow) +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  log(Rdamcrit) +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:log(Breslow) +
  SNstatus:multiple.fields
f.mi.full.Rec.5 <- Hmisc::fit.mult.impute(form.full.Rec.5, cph, xtrans=imputed.data,
                                 data=data.to.be.imputed,n.impute=m, pr=FALSE,
                                 fit.reps=TRUE, y=TRUE, x=TRUE, se.fit=TRUE)
stats::anova(f.mi.full.Rec.5)
summary(f.mi.full.Rec.5, Tot_SNs_pos=c(0, 1))
```

# Final model for recurrence selected by backward selection with p = 0.01
```{r, eval=TRUE}
c.Breslow <- mean(log(last.imputed.data.set$Breslow))
form.BS.Rec.5 <- S.Rec.5 ~
  SNstatus +
  Age.SN +
  Ulceration +
  Loc_CAT +
  I(log(Breslow)-c.Breslow) +
  log(Rdamcrit) +
  SNstatus:I(log(Breslow)-c.Breslow)
f.mi.BS.Rec.5 <- Hmisc::fit.mult.impute(form.BS.Rec.5,cph,xtrans=imputed.data,data=data.to.be.imputed,n.impute=m,
                           pr=FALSE,fit.reps=TRUE,y=TRUE,x=TRUE,se.fit=TRUE)
# backward selection
# round(stats::anova(f.mi.BS.Rec.5)[order(stats::anova(f.mi.BS.Rec.5)[, 'P']),], 3)
summary(f.mi.BS.Rec.5, Breslow=exp(c.Breslow))
coef(f.mi.BS.Rec.5)
stats::anova(f.mi.BS.Rec.5)
```

# Refitted full model for melanoma specific mortality
```{r, eval=TRUE}
form.full.MSM.5.refit <- S.MSM.5 ~
  SNstatus +
  Sex +
  Age.SN +
  Ulceration +
  Loc_CAT +
  Histology +
  log(Breslow) +
  multiple.fields +
  Tot_SNs_neg +
  Tot_SNs_pos +
  log(Rdamcrit) +
  Dewar +
  SNstatus:Sex +
  SNstatus:Age.SN +
  SNstatus:Ulceration +
  SNstatus:Loc_CAT +
  SNstatus:Histology +
  SNstatus:log(Breslow) +
  SNstatus:multiple.fields
f.mi.full.MSM.5.refit <- Hmisc::fit.mult.impute(form.full.MSM.5.refit,cph,xtrans=imputed.data,data=data.to.be.imputed,n.impute=m,
                                 pr=FALSE,fit.reps=TRUE,y=TRUE,x=TRUE,se.fit=TRUE)
summary(f.mi.full.MSM.5.refit, Tot_SNs_pos=c(0, 1))
stats::anova(f.mi.full.MSM.5.refit)
```

# Refitted final model for melanoma specific mortality
```{r, eval=TRUE}
form.BS.MSM.5.refit <- S.MSM.5 ~
  SNstatus +
  Age.SN +
  Ulceration +
  Loc_CAT +
  I(log(Breslow)-c.Breslow) +
  log(Rdamcrit) +
  SNstatus:I(log(Breslow)-c.Breslow)
f.mi.BS.MSM.5.refit <- Hmisc::fit.mult.impute(form.BS.MSM.5.refit,cph,xtrans=imputed.data,data=data.to.be.imputed,n.impute=m,
                                  pr=FALSE,fit.reps=TRUE,y=TRUE,x=TRUE,se.fit=TRUE)
summary(f.mi.BS.MSM.5.refit, Breslow=exp(c.Breslow))
stats::anova(f.mi.BS.MSM.5.refit)
```

# Calibrated final model for melanoma specific mortality
Fit disease specific mortality to the linear predictor of recurrence
```{r, eval=TRUE}
lp.BS <- f.mi.BS.Rec.5$linear
f.mi.BS.MSM.5 <- rms::cph(S.MSM.5~lp.BS,y=TRUE,x=TRUE)
MSM.cal.fact <- stats::coef(f.mi.BS.MSM.5)
MSM.cal.fact
stats::confint(f.mi.BS.MSM.5)
utils::write.table(paste0(sprintf("%.2f", stats::coef(f.mi.BS.MSM.5)), " [",
            sprintf("%.2f", as.numeric(stats::confint(f.mi.BS.MSM.5))[1]), "; ",
            sprintf("%.2f", as.numeric(stats::confint(f.mi.BS.MSM.5))[2]), "]"),
            file='Z:/Project Melanoom/PaperMelanoma/Results/calibration.MSS.txt', 
            row.names=FALSE, col.names=FALSE, sep=",")
```

@@

# C-index stratified by SN status
```{r, eval=TRUE}
for (outcome in c("Rec.5", "MSM.5.refit")){
  for (arm in c("Positive", "Negative")){
    f.mi.stratified <- eval(parse(text=paste0('f.mi.BS.', outcome)))
    if (outcome=="Rec.5"){
      S.5 <- S.Rec.5
    } else if (outcome=="MSM.5.refit"){
      S.5 <- S.MSM.5
    }
    S.5.subset <- S.5[last.imputed.data.set$SNstatus==arm,]

    cindex.stratified <- rep(0, m)
    cindex.se.stratified <- rep(0, m)
    for (i in 1:m){
      subset.imputed.data <- as.data.frame(mice::complete(imputed.data,i)[last.imputed.data.set$SNstatus==arm,])
      rc <- Hmisc::rcorr.cens(-predict(f.mi.stratified,newdata=subset.imputed.data, type="lp"), S.5.subset)
      cindex.stratified[i]<-rc["C Index"]
      cindex.se.stratified[i]<-rc["S.D."]/2
    }
    cindex.mi.stratified<-Rubin.combine(cindex.stratified,cindex.se.stratified)

    print(c(outcome, arm, sprintf('%.2f', cindex.mi.stratified$est),
    paste0("[", sprintf('%.2f', cindex.mi.stratified$est+qnorm(.025)*cindex.mi.stratified$se), 
           "; ", sprintf('%.2f', cindex.mi.stratified$est+qnorm(.975)*cindex.mi.stratified$se), "]")))
  }
}

```

@@

# save for Rshiny app
coef.Rec <- stats::coef(f.mi.BS.Rec.5)
center.Rec <- f.mi.BS.Rec.5$center
save(h0.Rec, h0.MSM, coef.Rec, c.Breslow, center.Rec, MSM.cal.fact,
     file=paste0('Z:/Project Melanoom/PaperMelanoma/Results/h0.Rec.MSM.Rdata'), compress=TRUE)
load(file=paste0('Z:/Project Melanoom/PaperMelanoma/Results/h0.Rec.MSM.Rdata'))
```

@@

#### Example to check probabilities with app
```{r, eval=TRUE}
patient.nr <- 115 # 395 and 396 = Negative, 397 and 398 = Positive, 30 = Head & neck, 115 has large Breslow
print(data.to.be.imputed[patient.nr, c("SNstatus", "Age.SN", "Ulceration", "Loc_CAT", "Breslow", "Rdamcrit")])

# calculate linear predictor
lp.score.Rec.true <- predict(f.mi.BS.Rec.5)[patient.nr]
lp.score.Rec.try <- predict(f.mi.BS.Rec.5, newdata=data.frame(SNstatus=data.to.be.imputed[patient.nr,"SNstatus"],
                                                            Age.SN=data.to.be.imputed[patient.nr,"Age.SN"],
                                                            Ulceration=data.to.be.imputed[patient.nr,"Ulceration"],
                                                            Loc_CAT=data.to.be.imputed[patient.nr,"Loc_CAT"],
                                                            Breslow=data.to.be.imputed[patient.nr,"Breslow"],
                                                            Rdamcrit=data.to.be.imputed[patient.nr,"Rdamcrit"]),
                                                            type="lp")
p.Rec.example <- fun.event(lp=lp.score.Rec.try, h0=h0.Rec)
p.MSM.example <- fun.event(lp=lp.score.Rec.try, h0=h0.MSM)
